One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change

### 2020-02-25 article4_jbr_diss.tex
submitted dissertation

\documentclass[review,fleqn]{elsarticle}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
%\usepackage{subfigure}
%\usepackage{subcaption}
%\usepackage{caption}
%\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filecontents}
\usepackage{tikz-qtree}
\usepackage{pdflscape}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{color, colortbl}

@@

%%%% TURN OFF PAGE NUMBER FOR INCLUSION IN THESIS
%\pagenumbering{gobble}
%%%%%%%

\begin{document}

@@

<<loading, results="asis", echo=FALSE >>=
setwd("/Users/larshovdanmolden/Documents/git/article4")
#library(xtable)
#library(semPLS)
#load("./data/resart4.RData")
r <- main$resmat
rm  <- main$resmatmed
l  <- main$loadings
ic <- data.frame(i[,c(1,4)]);colnames(ic) <- c("b","t")
ic$rn  <- 1:nrow(ic)
bb <- main$models$both
bm <- main$models$mmed
br <- main$models$rmed
#foolars=0.99
@

@@

% paper about the DC for MNC in india an dimpact on CA
%https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
The ultimate goal in the theory of dynamic capabilities ($DC$) is competitive advantage
\citep{Schilke2014,Helfat2007,Protogerou2012,Li2014,Efrat2018a,Mikalef2017,Davcik2016a}. Extant
theory argues that competitive advantage ($CA$) stem from resources and routines that are
well aligned to firms’ competitive environment
\citep{Helfat2007,Peteraf2013,Teece1997,Li2014,Jantunen201,Makkonen2014}. Dynamic
capabilities are a source of longer-term competitive advantage in this perspective through
its capacity to purposefully change these lower-level routines and capabilities
\citep{Winter2003,Helfat2011,Schilke2018,Pezeshkan2016b,Lin2014a}, also referred to as
ordinary, substantive, and zero-level routines and capabilities
\citep{Winter2003,Danneels2008,Collis1994}. As a group, these lower level routines and
capabilities are called 'behavioral objects of change' \citep{Verona2011,Zollo2016}, and constitutes an
important path through which DCs can enable competitive advantage \citep{Verona2011}.

@@

This role of {\bf conductor} is the conventional way of understanding dynamic capabilities. It
stems from one of the most common definitions \citep{Helfat2007} as well as the analogy of
the process as 'resource orchestration' \citep{Sirmon2011}. It is also found in the
empirical literature handling various functional forms of dynamic capabilities such as
acquisition targeting \citep{Bingham2015}, alliancing \cite{Schilke2014}, new product
development \cite{Danneels2008}, innovation capabilities \citep{Breznik2014}, marketing
capabilities \cite{Brune2009} and alliance capabilities \cite{Kale2002,kale2007}.

@@

Table \ref{tab:item} in the appendix describes the items used to operationalize the focal
constructs and their internal validity as measured by Dillon-Goldstein Rho which is the
preferred metric for this purpose \citep{Hair2019}. The results show that our key
constructs can be represented by the items in the survey, with a minor caveat. The measure
of strategic cognition as proactiveness loads only partly on one item (item
3). Statsistically, a loading of $\Sexpr{l[["lcog"]][3]}$ is on the weaker side of
traditional 'rules of thumb' \citep{Hair2010}, but from a theoretical stand point the
measure makes sense and is established in the literature \cite{covin2012}.

@@

\begin{table}[t]
  \caption{Descriptive statistics and correlation between key constructs and control
  variables.}
\label{tab:cor}
  <<corchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/cortab.rnw',results="asis">>=
@

@@

To test our hypotheses we then built a path-model from the latent variables we
constructed. This resulted in four models. The results from the structural model is
reported in figure \ref{fig:res} and table \ref{tab:res}. To estimate the standard errors
we ran simulations using bootstrapping and reported the simulation number, standard errors
and corresponding p-values. To evaluate the models we compared $R^2$ and $Q^2$ statistics
for model comparison. All these are reported in table \ref{tab:res}.

@@

The estimated models are based on the following specification:

\begin{align}
  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1} + \\
           & \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
\end{align}

@@

A final model includes an interaction term between $CAP_t$ and $COG_t$ to capture any
complementarity or substitution-effects these two may exhibit:

\begin{align}
  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} +  \\ \nonumber
  &\alpha_5 CAP_{i,1} \times  COG_{i,1} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
\end{align}

\section*{Results}
The main results of our analysis are depicted both in the graphical path diagrams (figure
\ref{fig:res}) and the regression table in table \ref{tab:res}. The use of PLS-SEM has
increased substantially in the realm of marketing \citep{hult2018} and strategic management
\citep{Hair2012,Valaei2017} and is the topic of special issues in leading journals \citep{Hair2020} (e.g. Journal of
Business Research call for papers in 2020). In this tradition we aim to present thorough
analysis of our models and largely follows the recommendations made in recent
contributions \citep{Hair2019}.

@@

\begin{table}[t]
  \caption{PLS-SEM results for key constructs}
\label{tab:res}
  \scriptsize
  <<child-demo, child='/Users/larshovdanmolden/Documents/git/article4/figure/restab.rnw'>>=
@
\begin{tablenotes}

@@

\begin{figure}\label{fig:med4}
 <<pathchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/medanalysisall.rnw',results="asis">>=
@
\caption{Mediation analysis - graphical representation}
\end{figure}

@@

Second, we suggested and demonstrated two different expressions of dynamic capabilities
(i.e. {\bf conductor} and {\bf coach}) as well as their workings in the dynamic
capabilities-competitive advantage nexus. This insight adds to the nascent work of
bringing cognition into broader strategic management field in general
\citep{Gavetti2012,Gavetti2005a} and dynamic capabilities in particular
\citep{Helfat2015,Arndt2018}. In particular, the evolutionary and resource based roots of
$DC$ theory has to a large extent been dominating the field \citep{Arndt2018,Peteraf2013}
leaving an important side of cognition \cite{Verona2011} and heuristics \cite{Arndt2015}
less explored. Particularly, the call for exploring new mediators of the $DC-CA$ nexus
\citep{Schilke2018} is particularly relevant to moving $DC$ theory forward. Our
conceptualization is thus an important contribution to this work. Bringing the notion of
simultanously separate and interpendent expressions of $DC$ has implications for
strategizing and decisions to pursue capability aquisition and development. As with the
case of Microsoft, our data shows that simultanously maintaining 'strategic cognition'
adds to outcome of the strategic change. Thus, managers who underestimate these effects
may very well end up delivering less value than they otherwise could.

@@

\section*{Appendix}

\begin{table}[t!]
  \label{tab:items}
    \caption{Core constructs and their measurement items. Factor
      loadings in parantheses}
    <<itemchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/itemtab.rnw',results="asis">>=
    @
    \begin{tablenotes}
      \tiny
      \item Dillon-Goldstein Rho is recommended as reliability measure
        for SEM-PLS \citep{Hair2019}.
    \end{tablenotes}
  \end{table}

>>>>

\documentclass[review,fleqn]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
%\usepackage{subfigure}
%\usepackage{subcaption}
%\usepackage{caption}
%\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filecontents}
\usepackage{tikz-qtree}
\usepackage{pdflscape}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{color, colortbl}

@@

%%%% TURN OFF PAGE NUMBER FOR INCLUSION IN THESIS
%\pagenumbering{gobble}
%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

% paper about the DC for MNC in india an dimpact on CA
%https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
The ultimate goal in the theory of dynamic capabilities ($DC$) is competitive advantage
\citep{Schilke2014,Helfat2007,Protogerou2012,Li2014,Efrat2018a,Mikalef2017,Davcik2016a}. Extant
theory argues that competitive advantage ($CA$) stem from resources and routines that are
well aligned to firms’ competitive environment
\citep{Helfat2007,Peteraf2013,Teece1997,Li2014,Jantunen2018,Makkonen2014}. Dynamic
capabilities are a source of longer-term competitive advantage in this perspective through
its capacity to purposefully change these lower-level routines and capabilities
\citep{Winter2003,Helfat2011,Schilke2018,Pezeshkan2016b,Lin2014a}, also referred to as
ordinary, substantive, and zero-level routines and capabilities
\citep{Winter2003,Danneels2008,Collis1994}. As a group, these lower level routines and
capabilities are called 'behavioral objects of change' \citep{Verona2011,Zollo2016}, and constitutes an
important path through which DCs can enable competitive advantage \citep{Verona2011}.

@@

This role of {\bf conductor} is the conventional way of understanding dynamic capabilities. It
stems from one of the most common definitions \citep{Helfat2007} as well as the analogy of
the process as 'resource orchestration' \citep{Sirmon2011}. It is also found in the
empirical literature handling various functional forms of dynamic capabilities such as
acquisition targeting \citep{Bingham2015}, alliancing \citep{Schilke2014}, new product
development \citep{Danneels2008}, innovation capabilities \citep{Breznik2014}, marketing
capabilities \citep{Brune2009} and alliance capabilities \citep{Kale2002,kale2007}.

@@

Table \ref{tab:item} in the appendix describes the items used to operationalize the focal
constructs and their internal validity as measured by Dillon-Goldstein Rho which is the
preferred metric for this purpose \citep{Hair2019}. The results show that our key
constructs can be represented by the items in the survey, with a minor caveat. The measure
of strategic cognition as proactiveness loads only partly on one item (item
3). Statsistically, a loading of $0.53$ is on the weaker side of
traditional 'rules of thumb' \citep{Hair2010}, but from a theoretical stand point the
measure makes sense and is established in the literature \cite{covin2012}.

@@

\begin{table}[t]
  \caption{Descriptive statistics and correlation between key constructs and control
  variables.}
\label{tab:cor}

\singlespacing
\tiny
\setlength{\tabcolsep}{3pt}
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Jan 28 12:23:38 2020
\begingroup\scriptsize
\begin{tabular}{lp{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}}
  \hline
 & Mean & SD & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
  \hline
1) $CA_1$ & 3.89 & 1.39 & 1 &  &  &  &  &  &  &  &  &  &  \\ 
  2) $CA_0$ & 3.88 & 1.47 & 0.38 & 1 &  &  &  &  &  &  &  &  &  \\ 
  3) $DC_0$ & 4.66 & 0.84 & 0.3 & 0.06 & 1 &  &  &  &  &  &  &  &  \\ 
  4) $CAP_1$ & 4.17 & 0.99 & 0.54 & 0.18 & 0.36 & 1 &  &  &  &  &  &  &  \\ 
  5) $CAP_0$ & 4.23 & 1.17 & 0.32 & 0.41 & 0.21 & 0.36 & 1 &  &  &  &  &  &  \\ 
  6) $COG_1$ & 4.63 & 1.15 & 0.45 & 0.06 & 0.39 & 0.46 & 0.25 & 1 &  &  &  &  &  \\ 
  7) $COG_0$ & 4.71 & 1.26 & 0.19 & 0.27 & 0.24 & 0.15 & 0.37 & 0.34 & 1 &  &  &  &  \\ 
  8) Size & 4.33 & 1.90 & 0.36 & 0.29 & 0.06 & 0.31 & 0.29 & 0.11 & 0.13 & 1 &  &  &  \\ 
  9) ln(Assets) & 10.01 & 2.03 & 0.35 & 0.33 & 0.06 & 0.32 & 0.26 & 0.08 & 0.11 & 0.87 & 1 &  &  \\ 
  11) Margin & -0.07 & 0.66 & 0.18 & 0.24 & 0 & 0.09 & 0.13 & -0.06 & -0.09 & 0.07 & 0.02 & 1 &  \\ 
  12) Age & 25.12 & 14.24 & 0.17 & 0.18 & -0.05 & 0.19 & 0.17 & -0.02 & -0.05 & 0.52 & 0.51 & 0.04 & 1 \\ 
   \hline
\end{tabular}
\endgroup

@@

To test our hypotheses we then built a path-model from the latent variables we
constructed. This resulted in four models. The results from the structural model is
reported in figure \ref{fig:med4} and table \ref{tab:res}. To estimate the standard errors
we ran simulations using bootstrapping and reported the simulation number, standard errors
and corresponding p-values. To evaluate the models we compared $R^2$ and $Q^2$ statistics
for model comparison. All these are reported in table \ref{tab:res}.

@@

The estimated models are based on the following specification:
\begin{align}
  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1} + \\
           & \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
\end{align}

@@

A final model includes an interaction term between $CAP_t$ and $COG_t$ to capture any
complementarity or substitution-effects these two may exhibit:
\begin{align}
  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} +  \\ \nonumber
  &\alpha_5 CAP_{i,1} \times  COG_{i,1} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
\end{align}

\section*{Results}
The main results of our analysis are depicted both in the graphical path diagrams (figure
\ref{fig:med4}) and the regression table in table \ref{tab:res}. The use of PLS-SEM has
increased substantially in the realm of marketing \citep{hult2018} and strategic management
\citep{Hair2012,Valaei2017} and is the topic of special issues in leading journals \citep{Hair2020} (e.g. Journal of
Business Research call for papers in 2020). In this tradition we aim to present thorough
analysis of our models and largely follows the recommendations made in recent
xcontributions \citep{Hair2019}.

@@

\begin{table}[t]
  \caption{PLS-SEM results for key constructs}
\label{tab:res}
  \scriptsize

\begin{tabular}{l*{5}{l}}

  \hline                                                                                                                                                                                \\[-0.5em]
                           & (1)                        & (2)                           & (3)                           & (4)                        & (5)                              \\ 
  %                        & \multicolumn{1}{c}{Direct} & \multicolumn{1}{c}{CAP model} & \multicolumn{1}{c}{COG model} & \multicolumn{1}{c}{BOTH model}                                \\
  \hline                                                                                                                                                                                \\
  \rowcolor{Gray}
                           & $\mathbf{CA_t}$            & $\mathbf{CA_t}$               & $\mathbf{CA_t}$               & $\mathbf{CA_t}$            & $\mathbf{CA_t}$                  \\     
  $DC_{t-1}$               & 0.246             & 0.134                & 0.126                & 0.083             & 0.061                  \\
                           & (5.52)  & (2.72)     & (2.49)     & (1.6)  & (1.12)       \\ [1em]
  $CAP_{t}$                &                            & 0.382                &                               & 0.324             & 0.331                  \\
                           &                            & (7.65)     &                               & (6.38)  & (7.24)       \\[1em]
  $COG_{t}$                &                            &                               & 0.301                & 0.188             & 0.225                  \\
                           &                            &                               & (5.27)     & (3.11)  & (3.66)       \\ [1em]
    $CAP_{t} \times COG_t$ &                            &                               &                               &                            & 0.093                  \\
                           &                            &                               &                               &                            & (2.04)       \\ [1em]
    \rowcolor{Gray}
                           & $\mathbf{}$                & $\mathbf{CAP_t}$              & $\mathbf{}$                   & $\mathbf{CAP_t}$           & $\mathbf{CAP_t}$                 \\
  $DC_{t-1}$               &                            & 0.237                &                               & 0.224             & 0.206                  \\ 
                           &                            & (4.12)     &                               & (3.38)  & (3.17)       \\[1em]
    \rowcolor{Gray}
                           & $\mathbf{}$                & $\mathbf{}$                   & $\mathbf{COG_t}$              & $\mathbf{COG_t}$           & $\mathbf{COG_t}$                 \\
  $DC_{t-1}$               &                            &                               & 0.325                & 0.331             & 0.329                  \\
                           &                            &                               & (5.23)    & (5.29) & (5.31)       \\  \\[-0.5em]
  \hline                                                                                                                                                                                \\[-0.5em]
  CA controls              & YES                        & YES                           & YES                           & YES                        & YES                              \\
  CAP controls             &                            & YES                           &                               & YES                        & YES                              \\
  COG controls             &                            &                               & YES                           & YES                        & YES                              \\
  $R^2$                    & 0.3   & 0.44      & 0.37      & 0.47   & 0.48                             \\
  $Q^2$                    & 0.2   & 0.31      & 0.25      & 0.32   & 0.31                             \\
 % GOF                      & round(r[13,2],2)   & round(r[13,3],2)      & round(r[13,4],2)      & round(r[13,5],2)   &                                  \\
 % BIC                      & round(r[14,2],1)   & round(r[14,3],1)      & round(r[14,4],1)      & round(r[14,5],1)   & round((r[14,5]*0.996),1) \\
  N                        & 240   & 232      & 240      & 232   & 232                              \\
  \hline
 % \multicolumn{4}{l}{\tiny Standardized coefficients. T-values in parantheses}                                                                                                         \\
\end{tabular}
\begin{tablenotes}

@@

\begin{figure}

\usetikzlibrary{arrows.meta}
% \begin{minipage}{.48\textwidth}
\begin{tabular}{cc}
  % \subcaption{DIRECT model}

 %\end{minipage}
 %\begin{minipage}{.48\textwidth}
   % \subcaption{CAP model}
  \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw,thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \node[mynode2,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.44$, $Q^2= 0.31$};

    \draw[-latex, line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
    fill=white] {$0.134^{*}$} (b.west);

    \draw[-latex, line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\footnotesize, align=center, fill=white] {$0.237^{*}$} (m.west);
    \draw[ -latex, line width=0.3mm] (m.east) -- node[text
    width=0.8cm,font=\footnotesize,align=center, fill=white] {$0.382^{*}$} (b.north);

    \draw[gray,-latex] (a.south) -- node[text width=1.3cm,font=\scriptsize, align=left, fill=none] {} (c.west);
    \draw[gray, -latex,line ] (c.east) -- node[text
    width=1.3cm,font=\scriptsize,align=right, fill=none] {} (b.south);

   \end{tikzpicture}
 %\end{minipage}
 %\begin{minipage}{.48\textwidth}
 %  \subcaption{COG model}
    &
  \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode2] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.37$, $Q^2= 0.25$};

    \draw[-latex, line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
    fill=white] {$0.126^{*}$} (b.west);

    \draw[gray,-latex] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=none] {} (m.west);
    \draw[gray, -latex,line ] (m.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=none] {} (b.north);

    \draw[-latex, line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=center, fill=white] {$0.325^{*}$} (c.west);
    \draw[-latex, line width=0.3mm] (c.east) -- node[text
    width=0.8 cm,font=\scriptsize,align=center, fill=white] {$0.301^{*}$} (b.south);

   \end{tikzpicture}
 %\end{minipage}
 %\begin{minipage}{.48\textwidth}
 %  \subcaption{FULL model}
  \\
  \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.47$, $Q^2= 0.32$};

    \draw[-latex,line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
    fill=white] {$0.083$} (b.west);

    \draw[-latex,line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.224^{*}$} (m.west);
    \draw[ -latex,line width=0.3mm ] (m.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.324^{*}$} (b.north);

    \draw[-latex,line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.331^{*}$} (c.west);
    \draw[-latex,line width=0.3mm ] (c.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.188^{*}$} (b.south);

   \end{tikzpicture}
    &
    \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \coordinate (CAf) at ([xshift=-1.25cm]b.west);
    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.48$, $Q^2= 0.31$};

    \draw[-latex,line width=0.3mm] (a.south east) -- node[above,text width=0.8cm,font=\scriptsize, align=left,
    fill=white] {$0.061$} (b.south west);

    \draw[-latex,line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.206^{*}$} (m.west);
    \draw[ -latex,line width=0.3mm ] (m.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.331^{*}$} (b.north);

    \draw[-latex,line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.329^{*}$} (c.west);
    \draw[-latex,line width=0.3mm ] (c.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.225^{*}$} (b.south);

     \draw[line width=0.3mm] (m.south east) to[bend left=20] node[text width=0.8cm,font=\scriptsize, align=center,
    fill=none] {} (c.north east);

    \draw[{Circle[black]}-latex,line width=0.3mm] (CAf.east) -- node[above, text width=0.2cm,font=\scriptsize, align=center,
    fill=white] {$0.093^{*}$} (b.west);

   \end{tikzpicture}
% \end{minipage}
\end{tabular}
\caption{Mediation analysis - graphical representation}
\label{fig:med4}
\end{figure}

@@

Second, we suggested and demonstrated two different expressions of dynamic capabilities
(i.e. {\bf conductor} and {\bf coach}) as well as their workings in the dynamic
capabilities-competitive advantage nexus. This insight adds to the nascent work of
bringing cognition into broader strategic management field in general
\citep{Gavetti2012,Gavetti2005a} and dynamic capabilities in particular
\citep{Helfat2015,Arndt2018}. In particular, the evolutionary and resource based roots of
$DC$ theory has to a large extent been dominating the field \citep{Arndt2018,Peteraf2013}
leaving an important side of cognition \citep{Verona2011} and heuristics \citep{Arndt2015}
less explored. Particularly, the call for exploring new mediators of the $DC-CA$ nexus
\citep{Schilke2018} is particularly relevant to moving $DC$ theory forward. Our
conceptualization is thus an important contribution to this work. Bringing the notion of
simultanously separate and interpendent expressions of $DC$ has implications for
strategizing and decisions to pursue capability aquisition and development. As with the
case of Microsoft, our data shows that simultanously maintaining 'strategic cognition'
adds to outcome of the strategic change. Thus, managers who underestimate these effects
may very well end up delivering less value than they otherwise could.

@@

\newpage
\section*{Appendix}

\begin{table}[h]
  \label{tab:items}
    \caption{Core constructs and their measurement items. Factor
      loadings in parantheses}

\scriptsize
\singlespacing
\setlist[itemize]{leftmargin=*}

\begin{tabular}{p{2cm} c p{9cm}}

\textbf{Construct}     & \textbf{Rho}               & \textbf{Items}\\ \toprule%
  \textbf{Dynamic} \\ \textbf{Capabilities} &\textbf{$0.89$} &\vspace{-5mm} 
                                                             \begin{itemize} 
                                                               \setlength\itemsep{-0.2em} 
                                                             \item Management receive frequent information about the employee's newly gained experiences ($0.69$)
                                                             \item Knowledge and experiences are shared a cross teams in the firm ($0.77$)
                                                             \item Knowledge and experiences are shared a cross teams in the firm ($0.76$)
                                                             \item Positive and negative experiences are shared between employees ($0.82$)
                                                             \item The employees are involved in discussions where the way of doing business is questioned ($0.79$)
                                                             \item The employees are encouraged to engage in critical discussions on how the company is conducting its business ($0.62$)
                                                             \item We conduct evaluations of "what has worked and what has not worked" in regards to larger projects etc ($0.61$)
                                                             \end{itemize} \\ \midrule%
 \textbf{Operating}                                                                            \\ \textbf{Capabilities} & \textbf{$0.84$}} & \vspace{-5mm} 
                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
                                                               \item The firm has better marketing competence than the competitors ($0.78$)
                                                               \item Compared to our competitors our firm is particularly skilled in customer service ($0.71$)
                                                               \itemCompared to our competitors our firm is particularly skilled in management and operations  ($0.86$)
                                                               \end{itemize} \\  \midrule%

   \textbf{Strategic} \\ \textbf{Cognition} & \textbf{$0.82$} & \vspace{-5mm} 
                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
                                                               \item Compared to our competitiors our firm typically refrain from action until competitors move, and then answer ($0.89$)
                                                               \item Compared to our competitors we are often first movers in introducing new products, services, administrative routines, production methods etc ($0.87$)
                                                               \item We relate to our competitors by adopting a "go get them" attitude. We are gonna win this ($0.53$)
                                                               \end{itemize} \\  \midrule%

   \textbf{Competitive} \\ \textbf{Advantage} & \textbf{$0.89$} & \vspace{-5mm} 
                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
                                                               \item The firm has better financial results than our competitors ($0.85$)
                                                               \item The firm has a stronger revenue growth than our competitors ($0.87$)
                                                               \item The firm has a larger market share than our competitors ($0.87$)
                                                               \end{itemize} \\  \bottomrule%

\end{tabular}
    \begin{tablenotes}
      \tiny
      \item Dillon-Goldstein Rho is recommended as reliability measure
        for SEM-PLS \citep{Hair2019}.
    \end{tablenotes}
  \end{table}
